Verified Nanopasses for Compiling Conditionals

### 2025-08-12 paper.tex
tweak

The third language replaces \lstinline{Let} bindings with assignment
expressions but retains the structured control-flow and
expression-oriented nature of the language. This language brings us
closer to x86 where variables are replaced by registers and stack
locations, which are mutable. The abstract syntax for assignment is
\lstinline{(Assign $x$ $e_1$ $e_2$)} where $e_1$ is the right-hand
side and $e_2$ is an expression to be executed after the assignment
(like the body of a \lstinline{Let}).  The \lstinline{Program} AST
node consists of the number of variables and an expression.

>>>>

The third language replaces \lstinline{Let} bindings with assignment
expressions but retains the expression-oriented and structured
control-flow nature of the language. This language brings us closer to
x86 where variables are replaced by registers and stack locations,
which are mutable. The abstract syntax for assignment is
\lstinline{(Assign $x$ $e_1$ $e_2$)} where $e_1$ is the right-hand
side and $e_2$ is an expression to be executed after the assignment
(like the body of a \lstinline{Let}).  The \lstinline{Program} AST
node consists of the number of variables and an expression.
